---
title: "Assignment 2"
author: "Amruta"
date: "11/10/2019"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

Q 1) Run the following code in R-studio to create two variables X and Y.
set.seed(2017)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y

Given :-

```{r}
set.seed(2017)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y

```

(a)	Plot Y against X. Include a screenshot of the plot in your submission. Using the File menu you can save the graph as a picture on your computer.  Based on the plot do you think we can fit a linear model to explain Y based on X? 

Solution :-

```{r}

plot(X,Y)

```

(b)	Construct a simple linear model of Y based on X. Write the equation that explains Y based on X. What is the accuracy of this model? 

Solution :-

* Formula : Y = 4.4655 + 3.6108 X 
* Accuracy = 65.17 %

```{r}

LM <- lm(formula = Y~X)
summary(LM)

```

(c)	How the Coefficient of Determination, R2, of the model above is related to the correlation coefficient of X and Y? 

Solution :-

* Co- efficient of Determination = Co-efficient of Correlation ^ 2
```{r}

cor(Y,X)
(cor(Y,X))^2

```

(d) Investigate the appropriateness of using linear regression for this case.

Solution :-

```{r}

qqnorm(LM$residuals,col="red")
qqline(LM$residuals)

```

* The residuals form an approximate horizontal band around the 0 line indicating homogeneity    of   error variance.
* There are few outliers.
* Thus we can say that model is linear to determine the appropriateness. 



Q 2)	We will use the ‘mtcars’ dataset for this question. The dataset is already included in your R distribution. The dataset shows some of the characteristics of different cars. 


(a)	James wants to buy a car.  He and his friend, Chris, have different opinions about the Horse Power (hp) of cars. James think the weight of a car (wt) can be used to estimate the Horse Power of the car while Chris thinks the fuel consumption expressed in Mile Per Gallon (mpg), is a better estimator of the (hp). Who do you think is right? Construct simple linear models using mtcars data to answer the question. 

Solution :-
 
```{r}

head(mtcars)
LM_mtcars <- lm(hp~mpg+wt, data = mtcars)
summary(LM_mtcars)

```
*The probability of getting weight of car (wt) equal to zero is 0.80217, whereas the probability of having Mile per Gallon (mpg) equal to zero is 0.00145; hence we can say that mpg is more statistically dependent on hp. Thus, Chris seems to be more appropriate than James. 



(b)	Build a model that uses the number of cylinders (cyl) and the mile per gallon (mpg) values of a car to predict the car Horse Power (hp). 

I]	Using this model, what is the estimated Horse Power of a car with 4 calendar and mpg of 22? 

Solution :-

```{r}

LM_mtcars1 <- lm(hp~cyl+mpg, data = mtcars)
summary(LM_mtcars1)

Predicted_Value_1 <- predict(LM_mtcars1, data.frame(cyl = 4, mpg = 22))
Predicted_Value_1

```
* Equation: hp = 54.067+ 23.979 * cyl - 2.775 * mpg
  hp = 54.067+ 23.979 * 4 - 2.775 * 22
  hp = 88.93
  
II]	Construct an 85% confidence interval of your answer in the above question.

Solution :-

*A confidence interval is a range of values, derived from sample statistics.
Building the model using the previous question values, and changing the CI to 85%

```{r}

Predicted_Value_2 <- predict(LM_mtcars1, data.frame(cyl = 4, mpg = 22), interval = "confidence", level = 0.85)
Predicted_Value_2

```

Q 3) For this question, we are going to use BostonHousing dataset. The dataset is in ‘mlbench’ package. 

Solution :-

```{r}

library(mlbench)
data(BostonHousing)

```

(a)	Build a model to estimate the median value of owner-occupied homes (medv)based on the following variables: crime crate (crim), proportion of residential land zoned for lots over 25,000 sq.ft (zn), the local pupil-teacher ratio (ptratio) and weather the whether the tract bounds Chas River(chas). Is this an accurate model? (Hint check R2 ) 

Solution :-

```{r}

LM_Boston_Housing <- lm(medv~crim+zn+ptratio+chas, data = BostonHousing)
summary(LM_Boston_Housing)

```
* The R-squared value here is 0.3599 which is relatively small; Hence this is not an accurate model.



(b)	Use the estimated coefficient to answer these questions? 	

[I]	Imagine two houses that are identical in all aspects but one bounds the Chas River and the other does not. Which one is more expensive and by how much? 

Solution :-

The house that bounds on the Chas River is expensive than that of the another identical house. It is expensive than the 4.58393 factor. 

  
[II].	Imagine two houses that are identical in all aspects but in the neighborhood of one of them the pupil-teacher ratio is 15 and in the other one is 18. Which one is more expensive and by how much? 

Solution :-

Calculating the expensive one between the two houses based on the pupil-teacher ratio, while  estimated coefficient is -1.49367. 

* When pupil-teacher ratio is 15 :-
49.91868 -1.49367 X 15 = 27.51368

* When pupil-teacher ratio is 18 :-
49.91868 -1.49367 X 18 = 23.03262

According to the above calculation, when the pupil to teacher ratio is 15 the house is more expensive than the with the 18. 



(c)	Which of the variables are statistically important (i.e. related to the house price)? Hint: use the p-values of the coefficients to answer.

Solution :-

All the variables are statistically important in determining the house price.



(d) Use the anova analysis and determine the order of importance of these four variables.

Solution :-

```{r}

anova(LM_Boston_Housing)

```

Order of Importance :-

* Crime crate is 6440.8
* Pupil to teacher ratio is 4709.5
* proportion of residential land zoned for lots over 25,000 sq.ft is 3554.3
* Chas River is 667.2